R Notebook

### 2020-12-13 AdvendOfCode2020/draft_post_3.Rmd
Resolução dos puzzle do dia 8 datasets

@@

A bright white bag, which can hold your shiny gold bag directly.
A muted yellow bag, which can hold your shiny gold bag directly, plus some other bags.
A dark orange bag, which can hold bright white and muted yellow bags, either of which could then hold your shiny gold bag.
A light red bag, which can hold bright white and muted yellow bags, either of which could then hold your shiny gold bag.

@@

@@

@@

>>>>

## Graph Generic Test

```{r}
library(tidygraph)
library(tidyverse)
library(ggraph)

g <- tibble(
  from = LETTERS[sample(1:8,12, replace = T)],
  to   = LETTERS[sample(1:8,12, replace = T)],
  dist = sample(1:8,12, replace = T)
) %>% 
  as_tbl_graph()

plotGraph <- function(g){
  g %>% 
    ggraph(layout = "kk") +
      geom_edge_fan(alpha=0.3) +
      geom_node_point(color="blue",alpha=0.8, size=8) +
      geom_node_text(aes(label=name), color="white") +
      theme_graph()
}

plotGraph(g)

g %N>%
  filter(name %in% c("G","H","C")) %>% 
  plotGraph()

g %>% 
  to_subgraph(name %in% c("G","H","C")) %>%
  .[[1]] %>% 
  class()

@@

```
A bright white bag, which can hold your shiny gold bag directly.
A muted yellow bag, which can hold your shiny gold bag directly, plus some other bags.
A dark orange bag, which can hold bright white and muted yellow bags, either of which could then hold your shiny gold bag.
A light red bag, which can hold bright white and muted yellow bags, either of which could then hold your shiny gold bag.
```

@@

# reads the input as a vector of strings
input <- readLines("./day07_test_01.txt")

# function to decode the string bag rules in a tibble
decodeBagRules <- function(.input){
  tibble(input=.input) %>% 
  # separates the bag from the content rule
  separate(input, into=c("bag","contains"), sep=" contain ") %>% 
  # for each back split the rule in different types of bag
  # we build a 'tidy' dataset, each line maps from a bag to a content
  group_by(bag) %>% 
  nest() %>% 
  ungroup() %>% 
  mutate( contains =  map(data,~unlist(str_split(.x,", "))) ) %>% 
  unnest(contains) %>% 
  select(-data) %>% 
  # now we splt the bag type and color 
  separate(bag, into = c("bag.type","bag.color"), sep = " ", extra = "drop") %>%
  # also for the content rule
  separate(contains, into = c("ctn.bag.qtd","ctn.bag.type","ctn.bag.color"), sep=" ", extra = "drop") %>% 
  # some adjust to bags with no content
  mutate( ctn.bag.qtd = if_else(ctn.bag.qtd=="no","0",ctn.bag.qtd) ) %>% 
  mutate( ctn.bag.qtd = as.integer(ctn.bag.qtd), 
          ctn.bag.type = if_else( ctn.bag.qtd==0, as.character(NA), ctn.bag.type),
          ctn.bag.color = if_else( ctn.bag.qtd==0, as.character(NA), ctn.bag.color) )
}

# transforms the strings in a data frame with the rules
bag.rules <- decodeBagRules(input)

@@

plotGraph(bag.graph)

@@

bag.subgraphs <- bag.graph %>% 
  all_simple_paths(from="shiny_gold") %>% 
  map(function(.p,.g){
    to_subgraph(.g, name %in% names(.p)) %>% 
      .[[1]] %E>% 
      as_tibble() %>% 
      pull(weight) %>% 
      sum()
  },.g=bag.graph)

bag.subgraphs %>% 
  map(function(.sg){
    class(.sg)
  })
